A multiverse analysis of the associations between internet use and well-being

### 2023-11-13 ms.Rmd
Work on reproducibility (#4)
Fixes to reproducibility & links

# Environment options
DATA_PATH_GWP <- Sys.getenv(
  "DATA_PATH_GWP"
)
DATA_PATH_GWP_CLEAN <- "data-raw/gwp.rds"
DATA_PATH_SYN <- Sys.getenv(
  "DATA_PATH_SYN"
)
MAX_CORES <- as.numeric(
  Sys.getenv(
    "MAX_CORES", 
    unset = parallel::detectCores(logical = FALSE)
  )
)

@@

# Wrangle GWP .sav file
if (file.exists(DATA_PATH_GWP) & !file.exists(DATA_PATH_GWP_CLEAN)) {

@@

# Create synthetic smaller dataset for code reproducibility.
if (!file.exists(DATA_PATH_SYN)) {
  dir.create(dirname(DATA_PATH_SYN), FALSE)

>>>>

# Environment options
MAX_CORES <- as.numeric(Sys.getenv("MAX_CORES"))
DATA_PATH_GWP <- Sys.getenv("DATA_PATH_GWP")
DATA_PATH_GWP_CLEAN <- Sys.getenv("DATA_PATH_GWP_CLEAN")
DATA_PATH_SYN <- Sys.getenv("DATA_PATH_SYN")
USE_GWP_DATA <- file.exists(DATA_PATH_GWP)

@@

# Wrangle GWP .sav file
if (USE_GWP_DATA & !file.exists(DATA_PATH_GWP_CLEAN)) {

@@

# Create synthetic smaller dataset for code reproducibility.
if (!file.exists(DATA_PATH_SYN) && file.exists(DATA_PATH_GWP_CLEAN)) {
  dir.create(dirname(DATA_PATH_SYN), FALSE)
